An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-02-25 journal/poly-embed.tex
Updated proofs for Prop 3

  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
\end{proof}
\begin{proof}[Via properties]
	\jessie{($L$ embeds $\ell \implies \risk{L} = \risk{\ell}$.)  $L$ embeds $\ell$ implies $\Gamma$ embeds $\gamma$, which is finite as $\ell$ is discrete.  By Prop 3, then we have $\{\gamma_r : r \in \R\} = \trim(\Gamma) = \{\Gamma_u : u \in \U \subset \reals^d \}$, where $\U$ is finite. Since $L$ embeds $\ell$}
	\jessie{$(\risk{L} = \risk{L} \implies L$ embeds $\ell$).  $\risk{L} = \risk{\ell}$ implies $\{\gamma_r : r \in \R\} = \trim(\Gamma)$, and therefore $\Gamma$ embeds $\gamma$, satisfying the first two conditions.  For the matching losses, this follows from the risks being equal...?}
\end{proof}

@@

Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses. \jessie{I think this is what's throwing me off 2.20.20}
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

	1 $\Rightarrow$ 2:
        \jessie{Intuition: $\Gamma$ embeds $\gamma$ implies their level sets are the same on facets, and $\trim(\Gamma)$ gets rid of any redundancies in $\Gamma$'s level sets.  Moreover, $\cup \trim(\Gamma) = \simplex$ since for all $\theta \in \trim(\Gamma)$, there is a $\gamma_r \in \gamma(\simplex)$ so that $\theta = \gamma_r$ and $\gamma$ is non redundant.}
        \jessie{Loss intuition: If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. }
	Since $\Gamma$ embeds $\gamma$, we know that $\gamma_r = \Gamma_{\varphi(r)}$.
	If we can show $\trim(\Gamma) = \{\Gamma_{\varphi(r)}\}_{r \in \R}$, then it suffices to see the result in terms of $\{\Gamma_{\varphi(r)}\}_{r \in \R}$.
	\hrule
	First, to see $\trim(\Gamma) \subseteq \Gamma_{\varphi(\R)}$.
	Take $\theta \in \trim(\Gamma)$.
	There must be some $u$ such that $\theta = \Gamma_u$.

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	Take some $u \not \in \varphi(\R)$.
	We want to show that there exists a $r \in \R$ such that $\Gamma_u \subseteq \Gamma_{\varphi(r)}$, and therefore, $\Gamma_u \not \in \trim(\Gamma)$.

	Consider any $p$ such that $p \in \Gamma(u)$.
	Since $\gamma$ is nondegenerate, we know $p \in \gamma(r)$ for some $r \in \R$, and by $\Gamma$ embedding $\gamma$, we also have $p \in \Gamma(\varphi(r))$.
	Therefore, $\Gamma(u) \subseteq \Gamma(\varphi(r))$.
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

	Next, to see $\Gamma_{\varphi(\R)} \subseteq \trim(\Gamma)$.
	Take $r \in \R$, and call $\theta = \Gamma_{\varphi(r)} = \gamma_r$.
	As $\gamma$ is nonredundant, we know there is no $r' \in \R$ such that $\gamma_{r'} = \Gamma_{\varphi(r')} \subseteq \theta$, and therefore $\theta \in \trim(\Gamma)$.
	\hrule
	Now that we have established $\trim(\Gamma) = \Gamma_{\varphi(\R)}$, we we show the result.
	As $\R$ is a finite set, so is $\Gamma_{\varphi(\R)}$ as it is finitely generated.
	Moreover, $\gamma$ is nondegenerate, we then have $\cup_\R \Gamma_{\varphi(r)} = \cup_\R \gamma_r = \simplex$.

	2 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional.  Take $\Theta = \trim(\Gamma)$.}

    \hrule \jessie{New}
    Each $\theta_i \in \Theta$ has some $u_i$ such that $\theta_i = \Gamma_{u_i}$.
    As $\cup \trim(\Gamma) = \cup_i \theta_i = \cup_i \Gamma_{u_i}$, we then have $\cup \Gamma_{u_i} = \simplex$

    If $\Gamma_{u_i}$ was not full-dimensional, then it would not be in $\trim(\Gamma)$

    \hrule

    Let $\R = \{u_1,\ldots,u_k\} \subseteq\reals^d$ be a set of distinct reports such that $\trim(\Gamma) = \{\Gamma_{u_1},\ldots,\Gamma_{u_k}\}$.
	Now as $\cup\,\trim(\Gamma) = \simplex$, for any $p\in\simplex$, we have $p\in\Gamma_{u_i}$ for some $u_i\in\R$, and thus $\Gamma(p) \cap \R \neq \emptyset$.
	We now satisfy the conditions of Lemma~\ref{lem:loss-restrict} with $\R_1 = \reals^d$ and $\R_2 = \R$.
	The property $\gamma:p\mapsto\Gamma(p)\cap\R$ is non-redundant by the definition of $\trim$, finite, and elicitable.
	Now from Lemma~\ref{lem:finite-full-dim}, the level sets $\Theta = \{\gamma_r:r\in\R\}$ are full-dimensional, and union to $\simplex$.
	Statement 3 then follows from the fact that $\gamma_r = \Gamma_r$ for all $r\in\R$.

	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
        Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.
\end{proof}
\begin{proof}[Original]
	Let $L$ elicit $\Gamma$.

@@

@@

>>>>

  For each $r\in\R$, let $p_r$ be a distribution in the interior of $\gamma_r$, and let $u_r \in \Gamma(p)$.
  Observe that, by definition of the Bayes risk and $\Gamma$, for all $u\in\reals^d$ the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports the epigraph $E_L$ of $-\risk{L}$ at the point $(p,-\inprod{p}{L(u)})$ if and only if $u\in\Gamma(p)$.
  Thus, the hyperplane $v \mapsto \inprod{v}{-L(u_r)}$ supports $E_L = E_\ell$ at the point $(p_r,-\inprod{p_r}{L(u_r)})$, and thus does so at the entire facet $\{(p,-\inprod{p}{L(u_r)}) : p\in\gamma_r\}$; by the above, $u_r \in \Gamma(p)$ for all such distributions as well.
  We conclude that $u_r \in \Gamma(p) \iff p \in \gamma_r \iff r \in \gamma(p)$, satisfying condition~\eqref{eq:embed-loss} for $\varphi : r \mapsto u_r$.
  To see that the loss values match, we merely note that the supporting hyperplanes to the facets of $E_L$ and $E_\ell$ are the same, and the loss values are uniquely determined by the supporting hyperplane.
  (In particular, if $h$ supports the facet corresponding to $\gamma_r$, we have $\ell(r)_y = L(u_r)_y = h(\delta_y)$, where $\delta_y$ is the point distribution on outcome $y$.)
\end{proof}

@@

Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} \jessie{= \{\Gamma_{\varphi(r)} : r \in \R\}} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
        \jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:elicitable-level-sets}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}

        Let $L$ elicit $\Gamma$.  
        If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  
		Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

        We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:elicitable-level-sets} and a corollary of the embedding definition).
        Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  
        Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

%	2 $\Rightarrow$ 1:
%	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
%	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
%	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

%	1 $\Rightarrow$ 3: \jessie{Intuition: Each $\theta \in \trim(\Gamma)$ is full dimensional by Lemma~\ref{lem:embedded-level-sets-trim} and equality of the set of embedded level sets of $\Gamma$ and set of level sets of $\gamma$.  Take $\Theta = \trim(\Gamma)$.}
%	Assume $\Gamma$ embeds a finite property $\gamma$.
%	Then for each $r \in \R$, we have $\Gamma_{\varphi(r)} = \gamma_r$, and therefore $\{\Gamma_{\varphi(r)} : r \in \R\} = \{\gamma_r : r \in \R\}$.
%	Chaining this with Lemma~\ref{lem:embedded-level-sets-trim}, we have $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
%	
%	\jessie{This is really the beginning of 2 $\Rightarrow 3$}
%	If there is a level set $\Gamma_{\varphi(\hat r)} \in \trim(\Gamma)$ that is not full-dimensional, then we can define an injection $\varphi'$ so that $\varphi' :\R \setminus \{\hat r\} \to \reals^d$ maps $r \mapsto \varphi(r)$.
%	(Iterate if there are multiple level sets that are not full-dimensional.)
%	Now take $\Theta = \{\Gamma_{\varphi'(r)} : r \in \R\}$.
%	We know each level set in $\Theta$ is full-dimensional by construction, and just need to show $\cup \Theta = \simplex$.
%	However, if there was a level set $\Gamma_{\varphi(\hat r)}$ that was not in $\trim(\Gamma)$ \jessie{\ldots}
	2 $\Rightarrow$ 3:
	\jessie{New attempt: show that $\Gamma$ elicitable and $\trim(\Gamma)$ finite implies each $\Gamma_u \in \trim(\Gamma)$ is full-dimensional. }

	We claim every $\theta \in \trim(\Gamma)$ is full-dimensional, then take $\Theta = \trim(\Gamma)$ and the result holds.
	Suppose there was a $u \in \reals^d$ so that $\Gamma_u \in \trim(\Gamma)$ and $\Gamma_u$ was not full-dimensional.
	The only case in which this happens is if $\Gamma_u$ spans two level sets, as anything that did not would be a subset of a full-dimensional level set in $\trim(\Gamma)$.
	However, if $\Gamma_u$ spans the relative interior of two full-dimensional level sets, we contradict the elicitability condition in Lemma~\ref{lem:elicitable-level-sets}.\jessiet{Need to be more careful here.}
	(If $\Gamma_u$ spans only the boundary of one level set, then we have that $\Gamma_u$ is a subset of the full-dimensional level set by closure of level sets of elicitable properties.)
	Therefore, we must have each $\Gamma_u \in \trim(\Gamma)$ full-dimensional if $\trim(\Gamma)$ is a finite set and $\Gamma$ is elicitable.

	3 $\Rightarrow$ 1: \jessie{Intuition: Take $\gamma = \Gamma|_{\varphi(\R)}$.}
    Let $\Theta = \{\theta_1,\ldots,\theta_k\}$.
	For all $i\in\{1,\ldots,k\}$ let $u_i\in\reals^d$ such that $\Gamma_{u_i} = \theta_i$.
	Now define $\gamma:\simplex\toto\{1,\ldots,k\}$ by $\gamma(p) = \{i : p\in\theta_i\}$, which is non-degenerate as $\cup\,\Theta = \simplex$.
	By construction, we have $\gamma_i = \theta_i = \Gamma_{u_i}$ for all $i$, so letting $\varphi(i) = u_i$ we satisfy the definition of embedding, namely statement 1.

\end{proof}

\begin{proof}[Original]
	Let $L$ elicit $\Gamma$.

@@

\proposedadd{ADDITIONS HERE:}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	\begin{itemize}
		\item [$\subseteq$] As $\gamma$ is finite (and implicitly non-redundant), we know that each level set of $\gamma$ must be full-dimensional. For all $r \in \R$, we know $\gamma_r = \gamma_{\varphi(r)}$ by the definition of embedding, so $\Gamma_{\varphi(r)} \in \trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}.
		\item[$\supseteq$] Take $u'$ so that $\Gamma_{u'} \not \in \{\Gamma_u : u \in \varphi(\R)\}$.
		We proceed in 3 cases: first, if there exists a $u$ such that $\Gamma_{u'} \subsetneq \Gamma_u$, then $\Gamma_{u'} \not \in \trim(\Gamma)$.
		If there is a $u \in \varphi(\R)$ such that $\Gamma_u = \Gamma_{u'}$, then we have $\Gamma_{u'}$ in the original set, as well as in $\trim(\Gamma)$ by Lemma~\ref{lem:fdls-in-trim}, since $\Gamma_{u'}$ must then be full-dimensional.
		In the final case, we have $\Gamma_{u'}$ not a subset of any $\Gamma_\varphi(r)$.
		Then by nondegeneracy of $\gamma$ (and in turn, of $\Gamma$) spans the interior of multiple level sets in $\{\Gamma_u : u \in \varphi(\R)\}$, which contradicts the elicitability of $\Gamma$ by Lemma~\ref{lem:elicitable-level-sets}.
		Thus, we cannot observe this case.
	\end{itemize}
\end{proof}

\begin{lemma}\label{lem:fdls-in-trim}
	If $\theta$ is a full-dimensional level set (in the simplex) of the elicitable property $\Gamma$, then $\theta \in \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $u$ be the report such that $\theta = \Gamma_u$.
	If there is a $u'$ so that $\Gamma_u = \Gamma_{u'}$, one of the level sets is in $\trim(\Gamma)$, and then we have $\theta$ equal to that level set.
	If $\Gamma_u \subsetneq \Gamma_{u'}$, then either $\Gamma_u$ is not a full-dimensional level set or $\Gamma_u \cap \Gamma_{u'}$ is full-dimensonal.
	If $\Gamma_u$ is not full-dimensional, then we contradict our assumption.
	If $\Gamma_u \cap \Gamma_{u'}$ is full dimensional, then we contradict our elicitability condition (Lemma~\ref{lem:elicitable-level-sets}).
	Therefore, full-dimensional level sets of an elicitable property must be in the trim operation of the same property.
\end{proof}

\begin{lemma}\label{lem:elicitable-level-sets}
	Let $\Gamma$ be an elicitable property.
	For all $p \in \simplex$, we have $|\Gamma(p)| > 1 \iff \exists r \in \Gamma(p)$ such that $\Gamma_{r'} \subseteq \Gamma_r$ for all $r' \in \Gamma(p)$.
\end{lemma}
\begin{proof}
	\jessie{TODO: argument on subgradients of the concave score over the loss.}
\end{proof}

@@

\begin{theorem}
	Every polyhedral loss embeds a finite elicitable property. \jessie{type check??}
	Moreover, a polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a property which refines $\gamma$.
\end{theorem}
\begin{proof}
	Let $\L$ be a polyhedral loss, and $\Gamma$ by the unique property it elicits.
	By Theorem~\ref{thm:poly-embeds-discrete}, we know there is a discrete loss $\ell$ embedded by $L$.
	Take $\gamma$ to be the finite property elicited by $\ell$.
\end{proof}
\begin{proof}[Original]
	Let $L:\reals^d\to\reals^\Y_+$ be a polyhedral loss.
	For all $p$, let $P(p)$ be the epigraph of the convex function $u\mapsto \inprod{p}{L(u)}$.
	From Lemma~\ref{lem:polyhedral-pd-same}, we have that the power diagram induced by the projection of $P(p)$ onto $\reals^d$ is constant whenever $p\in\inter\simplex$.
	Let $q\in\inter\simplex$ be the uniform distribution on $\Y$, and $V_\Y$ be the set of vertices of $P(q)$ projected onto $\reals^d$.
	By the above, this set is the same had we replaced $q$ by any $p\in\inter\simplex$.
